Would NEMO benefit from using the \psyclone\ system?

### 2017-01-10 docs/NEMO/psyclone_and_nemo.tex
Update NEMO doc to reflect PSyclones current functionality.

\psyclone\ is currently being developed as part of the GungHo project
and forms a component of the Dynamo (the prototype dynamical core)
build system. \psyclone\ can currently generate correct sequential code
for Dynamo and supports transformations such as loop colouring, loop
fusion, OpenMP and module inlining. We are currently working
on OpenACC transformations and are about to start work on MPI support.

@@

We believe that there are three possible places in which to locate the
k loop in NEMO:

@@

We believe therefore that the least intrusive and most performant way
to introduce \psyclone\ to NEMO would be option (2). This is dependent
on it being possible to construct a formal description of the majority
of k loops (i.e. the values to use for the loop bounds) within NEMO.

@@

One of the key advantages of the \psyclone\ system is that it is
possible for it to co-exist with existing code structures including
infrastructure that makes use of MPI.

>>>>

\psyclone\ is being developed as part of the GungHo project
and forms a component of the LFRic (the prototype Met Office
atmosphere model implementing GungHo science) build
system. \psyclone\ can currently generate correct sequential and
MPI-parallel code for Dynamo and supports transformations such as loop
colouring, loop fusion, OpenMP and module inlining. We plan to
introduce support for OpenACC along similar lines to the OpenMP
transformations.

@@

We believe that there are three possible places in which to locate the
$k$ loop in NEMO:

@@

We believe therefore that the least intrusive and most performant way
to introduce \psyclone\ to NEMO would be option (2). This is dependent
on it being possible to construct a formal description of the majority
of $k$ loops (i.e. the values to use for the loop bounds) within NEMO.

@@

One of the key advantages of the \psyclone\ system is that it is
possible for it to co-exist with existing code structures, including
infrastructure that makes use of MPI.
